SafeNet: A European database of plant-pollinator interactions

### 2024-02-16 Manuscript/Ms.qmd
Author list ready

dates1 = dates %>% 
group_by(Study_id, Network_id, Sampling_method) %>% 
summarise(Min_date = min(Date), 
          Max_date= max(Date), 
          Sampling_days = n_distinct(Date)) %>% 
mutate(Sampling_period = as.numeric(Max_date - Min_date)) %>% 
mutate(Study_number = as.integer(str_extract(Study_id, "[^_]+")), 
       .before=Study_id) %>% 
arrange(Study_number) %>% 
mutate(Sampling_period = case_when(!is.na(Sampling_period) ~ Sampling_period + 1,
TRUE ~ NA)) %>% 
mutate(Sampling_days = case_when(!is.na(Sampling_period) ~ Sampling_days,
TRUE ~ NA))
#Extract min and max number of sampling days
min_sampling_day = dates1 %>% pull(Sampling_days) %>% min(na.rm = TRUE)
max_sampling_day = dates1 %>% pull(Sampling_days) %>% max(na.rm = TRUE)
#Extract average of sampling days across networks and studies
average_sampling_days = dates1 %>% 
ungroup() %>% 
group_by(Study_id) %>% 
summarise(mean_sampling_days = mean(Sampling_days, na.rm = TRUE)) %>% 
ungroup() %>% 
summarise(mean(mean_sampling_days, na.rm = TRUE)) %>% 
pull()
#Check number of distinct sampling sites
n_sites = data %>% 
select(Latitude, Longitude) %>% 
distinct() %>% 
nrow(.)
#Check number of distinct bioregions
n_bioregion = data %>% 
select(Bioregion) %>% 
distinct()  %>% 
nrow(.)
```

>>>>

dates1 = dates %>% 
group_by(Study_id, Network_id, Sampling_method) %>% 
summarise(Min_date = min(Date), 
          Max_date= max(Date), 
          Sampling_days = n_distinct(Date)) %>% 
mutate(Sampling_period = as.numeric(Max_date - Min_date)) %>% 
mutate(Study_number = as.integer(str_extract(Study_id, "[^_]+")), 
       .before=Study_id) %>% 
arrange(Study_number) %>% 
mutate(Sampling_period = case_when(!is.na(Sampling_period) ~ Sampling_period + 1,
TRUE ~ NA)) %>% 
mutate(Sampling_days = case_when(!is.na(Sampling_period) ~ Sampling_days,
TRUE ~ NA))
#Extract min and max number of sampling days
min_sampling_day = dates1 %>% pull(Sampling_days) %>% min(na.rm = TRUE)
max_sampling_day = dates1 %>% pull(Sampling_days) %>% max(na.rm = TRUE)
#Extract average of sampling days across networks and studies
average_sampling_days = dates1 %>% 
ungroup() %>% 
group_by(Study_id) %>% 
summarise(mean_sampling_days = mean(Sampling_days, na.rm = TRUE)) %>% 
ungroup() %>% 
summarise(mean(mean_sampling_days, na.rm = TRUE)) %>% 
pull()
#Check number of distinct sampling sites
n_sites = data %>% 
select(Latitude, Longitude) %>% 
distinct() %>% 
nrow(.)
#Check number of distinct bioregions
n_bioregion = data %>% 
select(Bioregion) %>% 
distinct()  %>% 
nrow(.)
#Read author list 
authors = readr::read_csv("../Data/Manuscript_info/Authorship_ordered.csv")
#Print authors
authors = authors %>% 
summarise(col = paste(Coauthor_name_aff, collapse="| ")) %>% 
pull()
#Read affiliation list 
aff_list = readr::read_csv("../Data/Manuscript_info/Affiliation_list.csv")
aff_list = aff_list %>% 
summarise(col = paste0(Aff_number_Aff, "\\",sep="")) %>% 
pull()

\vspace*{-12mm}

`r authors`

**Corresponding author**= barragansljose@gmail.com\
*All authors excluding the first three and last are ordered alphabetically*

\begingroup
\small

`r aff_list`

\small
\endgroup
